Effects of the body force on the evacuation dynamics

### 2020-01-14 paper.tex
agregue grafico de blocking clusters vs vd para distintos kn

To conclude this section, we want to emphasize that increasing body stiffness has a significant impact on the evacuation dynamics. The stiffer pedestrians are, the less they touch to each other (less degree and less overlap). This yields a reduction of an increment of the speed, which reduces the evacuation time. \\

>>>>

The clusterization of the pedestrians has a significant impact on the blocking clusters (the group of pedestrians that clog the exit).  Fig.~\ref{pbc_vs_vd_multi_kn} shows the blocking cluster existence probability as a function of the desired velocity for different $k$ values. The blocking clusters occur more often when the desired velocity increases because increasing $v_d$ increase the density in the area close to the exit. The most remarkable fact of Fig.~\ref{pbc_vs_vd_multi_kn} is that increasing the stiffness reduces the blocking cluster existence for a fixed value of $v_d$. Under these conditions, the blocking clusters strictly govern the evacuation dynamics~\cite{dorso_2005}. Thus, increasing the stiffness reduces the blocking cluster existence, which improves the evacuation time.\\

\begin{figure}[htbp!]
\centering
\includegraphics[width=0.7\columnwidth]
{./pbc_vs_vd_multi_kn.eps}
\caption{\label{pbc_vs_vd_multi_kn} Blocking cluster existence probability as a function of $v_d$ for different stiffness levels (see label). The probability is calculated as the amount of time a blocking cluster is present divided by the overall simulation time. The result correspond to a bottleneck geometry with 225 pedestrians in periodic boundary conditions (re-injection of pedestrians once the exited the room). The simulation lasted $t_f =$ 1000~s. }
\end{figure}

To conclude this section, we want to emphasize that increasing body stiffness has a significant impact on the evacuation dynamics. The stiffer pedestrians are, the less they touch to each other (less degree and less overlap). This phenomenon yields a reduction of the existence of the blocking clusters, which reduces the overall evacuation time. \\
\\
